DNSKEY Management

### 2012-12-07 paper/paper.tex
Corrections and precisions.

\section{Introduction}
DNSSEC is gradually being deployed in the Internet. However, managing
the cryptographic keys required for the secure delegation provided by
DNSSEC is not always entirely trivial.

@@

\subsection{Chain of Trust\wbjp}
The goal of DNSSEC is to allow resolvers -- any person or process querying a DNS server -- to ensure the authenticity of the reply. Namely, in standard DNS, nothing guarantees the resolvers that his query's answer has not been modified or really originated from a legitimate server.

@@

In the DNS world, the \emph{friend} we trust is the so-called root authority -- the root domain -- of whom we know the public key in advance.

@@

%% TODO this is not entirely true. The DNSKEYs are in the zone
%% itself. Only their signatures are in the parent zone.
\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch.|'s public key, obtained from \verb|epfl.ch.|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch.|'s public key -- returned by \verb|epfl.ch.| with its public key, retrieved from the \verb|ch.| DNS server;
\item Again, verify \verb|ch.|'s responses by getting its public key from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

The registries are the entities serving the records for a zone. For example, SWITCH is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch.| is the school in itself (its IT-department to be precise\footnote{As a \emph{whois} query on the epfl.ch domain will show you.}), for example.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch.| zone is signed it is easy for the school to sign \verb|www.epfl.ch.|. However, if the domain to be signed was \verb|epfl.ch.| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by SWITCH or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

@@

\begin{description}
\item[Key Signing] Services that will handle the zone signing and key rollovers are available\footnote{like this registrar: \url{http://registrars.nominet.org.uk/registration-and-domain-management/dns/dnssec-signing-service}}.
\item[Hosting] Countless hosting services are available, many of which are proposed by actual registrars. Some of them can also propose DNSSEC to their customers, in addition to the standard DNS service they also provide.
\end{description}

@@

\begin{itemize}
\item[-] The transferred private key is not totally \emph{private} anymore, as now both the old and new service provider know it;
\item[-] Newly generated keys will require an update of the parent zone, and this might happen outside of normally planned rollover periods.
\end{itemize}

@@

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating the DNS record. Even with improvements like incremental signing, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
%TODO find good ref on this.

@@

Again, this teardown must happen in a synchronous way -- requiring additional effort with regard to DNS -- as resolvers will perceive the domain to be \emph{broken} as long as all involved parties are in a incoherent state.

>>>>

\section{Introduction}
DNSSEC is gradually being deployed throughout the Internet. However, managing
the cryptographic keys required for the secure delegation provided by
DNSSEC is not always entirely trivial.

@@

\subsection{Chain of Trust\wbjp}
The goal of DNSSEC is to allow resolvers -- any person or process querying a DNS server -- to ensure the authenticity of the reply. Namely, in standard DNS, nothing guarantees the resolvers that his query's answer has not been modified during the transmission or really originated from a legitimate server.

@@

In the DNS world, the \emph{friend} we trust is the so-called root authority -- the root domain -- of whom we know the public key in advance, so we can verify anything it signed.

@@

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch.|'s public key ;
\item Check \verb|lacal.epfl.ch.|'s public key authenticity by obtaining its signature from \verb|epfl.ch.|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch.|'s public key signature -- returned by \verb|epfl.ch.| with its public key;
\item Check \verb|epfl.ch.|'s public key against the corresponding signature served by \verb|ch.|;
\item Again, verify \verb|ch.|'s responses by getting its public key signature from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

The registries are the entities serving the records for a zone. For example, SWITCH is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch.| is the school in itself (its IT-department, to be precise\footnote{As a \emph{whois} query on the epfl.ch domain will show you.}), for example.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch.| zone is signed it is easy for the school to sign \verb|www.epfl.ch.|. However, if the domain to be signed was \verb|epfl.ch.| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.|, managed by SWITCH, or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well vary among different registrars and TLD's.

@@

\begin{description}
\item[Key Signing] Services that will handle the zone signing and key rollovers are available\footnote{Like this registrar: \url{http://registrars.nominet.org.uk/registration-and-domain-management/dns/dnssec-signing-service}}.
\item[Hosting] Countless hosting services are available, many of which are proposed by actual registrars. Some of them can also propose DNSSEC to their customers, in addition to the standard DNS service they also provide.
\end{description}

@@

\begin{itemize}
\item[-] The transferred private key is not totally \emph{private} anymore, as now both the old and new service provider know it;
\item[-] Newly generated keys will require an update of the parent zone
\end{itemize}

In both cases,  this \emph{transfer} scenario will require a certain level of cooperation between two concurrent companies.

@@

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating a DNS record. Even with improvements like incremental signing, the computational requirements are significant and must be considered when a registrar wishes to enable DNSSEC.
%TODO find good ref on this.

@@

Again, this teardown must happen in a synchronous way -- requiring additional efforts compared to standard DNS -- as resolvers will perceive the domain to be \emph{broken} as long as all involved parties are in an incoherent state.
